PK object batch mode trial

### 2023-08-16 data-raw/batchMode_trial_gpm.Rmd
Plots for R-squared, fold errors, and RMSEs

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
                subjects.species_harmonized %in% "hamster",
                studies.administration_route_normalized %in% "iv")
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")

@@

@@

plot(my_pk,
     method = "L-BFGS-B",
     print_out = TRUE)
# Joint
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

fe_df <- fold_errors(my_pk)
# Something wrong with the summary method... maybe only use detects?
fold_errors_all <- fe_df %>%
  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
  dplyr::filter(Detect %in% TRUE) %>%
  dplyr::group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
  dplyr::mutate(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
                median_FoldErr = median(Fold_Error, na.rm = TRUE),
                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error)) %>%
  dplyr::select(Time, Fold_Error,
                avg_FoldErr, median_FoldErr, within_2fold) %>%
  tidyr::nest(full_fold_errors = c(Time, Fold_Error))

@@

@@

>>>>

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID8025337")

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9022360")

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
                subjects.species_harmonized %in% "hamster",
                studies.administration_route_normalized %in% "iv")
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID1043881",
                                                              "DTXSID8020541",
                                                              "DTXSID6034849"),
                subjects.species_harmonized %in% "rat")

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")

@@

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID1034187",
                                                              "DTXSID2021315",
                                                              "DTXSID3032179",
                                                              "DTXSID4020533"))

@@

plot(my_pk, method = "L-BFGS-B",
     n_interp = 50) -> pl

plot(my_pk,
     method = "L-BFGS-B",
     n_interp = 50,

     print_out = TRUE)
# Joint
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

winning_model <- get_winning_model(my_pk)
fe_df <- fold_errors(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
# May need to change the use_scale_conc defaults
r2_df <- rsq(my_pk, method = "L-BFGS-B", use_scale_conc = FALSE) %>%
  inner_join(winning_model)
myAIC <- AIC(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
myRMSE <- rmse(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)

# Something wrong with the summary method... maybe only use detects?
fold_errors_all <- fe_df %>%
  dplyr::filter(Detect %in% TRUE) %>%
  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
  dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
                median_FoldErr = median(Fold_Error, na.rm = TRUE),
                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error))

myRMSE <- myRMSE %>%
  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
  dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE),
                median_MSE = median(RMSE^2, na.rm = TRUE))

my_df <- left_join(fold_errors_all, r2_df) %>% inner_join(myAIC) %>% inner_join(myRMSE)
mypl <- ggplot(data = my_df,
               aes(
                 x = within_2fold,
                 y = Rsq,
                 color = model
               )) + geom_point() +
  geom_abline(slope = 1, color = "red4", linetype = "longdash") +
  scale_color_manual(values = c("#0398FC", "#D68E09", "black")) +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())
ggExtra::ggMarginal(mypl, groupFill = TRUE,
                    type = "histogram",
                    xparams = list(binwidth = 0.05),
                    yparams = list(binwidth = 0.05))
ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "R2_within2fold_comparison.png"),
       plot = ggExtra::ggMarginal(mypl, groupFill = TRUE,
                    type = "histogram",
                    xparams = list(binwidth = 0.05),
                    yparams = list(binwidth = 0.05)),
       height = 5,
       width = 5,
       units = "in")

ggplot(data = rmse(my_pk, method = "L-BFGS-B",
                   rmse_group = vars(Route, Media, Dose),
                   use_scale_conc = FALSE) %>%
         inner_join(winning_model) %>%
         mutate(RMSE = ifelse(RMSE == 0, 1E-6, RMSE)),
               aes(
                 x = log10(RMSE),
                 color = model,
                 fill = model
               )) + 
  geom_histogram(bins = 100) +
  # geom_freqpoly(aes(groups = paste(Chemical, Species)),
  #               color = "black",
  #               bins = 5) +
  scale_color_manual(values = c("#0398FC", "#D68E09", "grey10")) +
  scale_fill_manual(values = c("#0398FC", "#D68E09", "grey10")) +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  facet_grid(rows = vars(model),
             cols = vars(Route)) +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        strip.background = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())
ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RMSEs_winningmodel_LBFGSB_zero1E-6_RouteFacet_notNormalized.png"),
       height = 4,
       width = 6,
       units = "in")

 rmse(my_pk, method = "L-BFGS-B",
      rmse_group = vars(Route, Media, Dose)) %>%
   inner_join(get_winning_model(my_pk, method = "L-BFGS-B")) %>%
   count(model)

rmse(my_pk, method = "L-BFGS-B",
                   rmse_group = vars(Route, Media, Dose)) %>%
  inner_join(winning_model) %>%
  filter(RMSE < 0.01, RMSE > 0.0001, Route == "oral", model == "model_1comp") %>%
  group_by(Chemical, Species, Route, Media) %>%
  mutate(group_size = n(),
         logRMSE = log10(RMSE)) %>%
  arrange(Chemical, Species, Route, Media, RMSE) %>%
  View()

@@

ggplot() +
  geom_histogram(data = fold_errors_all, 
                 aes(x = within_2fold),
                 bins = 100) +
  geom_vline(xintercept = fold_errors_all %>%
               filter(Chemical == "DTXSID8025337") %>%
               pull(within_2fold)) +
  scale_x_log10()

fold_errors_all %>% ungroup() %>%
  mutate(per_rank = rank(within_2fold)/n()) %>%
  filter(Chemical == "DTXSID8025337") %>%
  dplyr::select(-full_fold_errors)

@@

# Evaluate at level of Cmax and AUC RMSE
my_tkstats <- eval_tkstats(my_pk, method = "L-BFGS-B")
my_tkstats %>%
  dplyr::select(Chemical, Species, Route, Media, model, method,
                starts_with("Cmax"),
                starts_with("AUC")) %>%
  distinct() %>% 
  filter(is.finite(Cmax.tkstats), is.finite(AUC_inf.tkstats),
         is.finite(Cmax.nca), is.finite(AUC_inf.nca)) %>%
  ggplot(aes(x = Cmax.tkstats/Cmax.nca,
             y = AUC_inf.tkstats/AUC_inf.nca)) +
  geom_point() +
  geom_abline(slope = 1, color = "red4")
